### 2016-01-25 weeklyReport/problem.tex
end of build error idea,switch to repair.1-21-16

\section{Problem}  
To obtain necessary functionality, developers often use third-party libraries. Due to the complexity of current software systems, the dependency issue arises when the system depend on different and incompatible versions of the same library. This issue, called  `dependency hell'~\cite{wiki:hell} may break other dependencies or push the problem to another set of libraries.  We use an example to illustrate how the `dependency hell' causes a build error, how it is localized, how it is fixed in the next session.

@@

@@

We propose an approach to check compatibility on the interfaces that use different versions for the same libraries, which has the possibility to introduce `dependency hell'. Instead of strict backward compatibility checker for the entire class~\cite{Welsch:backward12}, we regard it as safe if the used API is compatible for the other version in the current usage context. We make this trade-off because developers often embrace changes, making multiple versions incompatible to each other~\cite{bogart:backward}. To save build time and space,  we include multiple versions of the files from the same library only if they are incompatible with each other, instead of maintaining multiple versions for the same library at the same time. To save time for analysis, we only consider the API calls when it has the possibility to generate `dependency hell', since there is no need to check the dependency issue if the libraries are consistent used in the system with a single version.

>>>>

\section{Problem}  
To obtain necessary functionality, developers often use third-party libraries. Due to the complexity of current software systems, the dependency issue arises when the system depend on different and incompatible versions of the same library. This issue, called  `dependency hell'~\cite{wiki:hell} may break other dependencies or push the problem to another set of libraries. When developers try to introduce a new library or upgrade existing ones, then other applications on their system might suddenly break as the newly-introduced libraries are not backward-compatible to the existing libraries. We use an example to illustrate how the `dependency hell' causes a build error, how it is localized, how it is fixed in the next session.

@@

\section{Related Work}

When two versions of the same library occur, Maven selects the closest library  in the tree of dependencies by default~\cite{maven:depend} (e.g., if dependencies for A, B, and C are defined as A -> B -> C -> D 2.0 and A -> E -> D 1.0, then D 1.0 will be used when building A because the path from A to D through E is shorter). User is able to manually exclude or force Maven to use a specific version, but the correctness is not guaranteed~\cite{maven:note}. Maven Enforcer Plugin checks a set of build rules including a Ban-Transitive-Dependency rule that detects all transitive dependencies conflicts and force users to resolve all conflicts. The Enforcer Plugin only checks the \codefont{groupid}, \codefont{artifactid}, and \codefont{version} declared in the configuration file (\todo{Lisa: though I don't know if we need to check semantics or compatibility of different versions, I leave this limitation for future reference}), and it does not help developers fix the conflicts without breaking any other parts of the system.
The majority of existing build systems model dependencies identical to Maven. Examples include Gradle, MSBuild, Make, and CloudMake. The features that make them different are unrelated to dependency management, but on syntax of build scripts and parallelization.

Bazel is a new build system developed by Google that advertises parallelization and correctness~\cite{bazel:depend}. Bazel does not allow transitive dependency and only reads dependencies listed in from the root dependency declaration file. This means that if your project (A) depends on another project (B) which list a dependency on project C in its WORKSPACE file, both transitive dependencies from B and C should be added to the WORKSPACE file. This can balloon the file size, but hopefully limits the chances of having one library include C at version 1.0 and another include C at 2.0. But they also assume that users can provide correct configuration and select correct versions of libraries.

Package managers in operating system also encounter similar dependency management problem. To deal with destructive upgrade and multi-distribution support in Linux products, Nix ~\cite{nix} provides a co-existing package management mechanism to store a source package in its own directory, instead of a global location that share across the entire system. However, this might not work in build system like Maven, as with transitive dependencies, the graph of included libraries can quickly grow quite large~\cite{maven:depend}.

@@

%We propose an approach to verify the safety of upgrading and

%We propose an approach to check compatibility on the interfaces that use different versions for the same libraries, which has the possibility to introduce `dependency hell'. Instead of strict backward compatibility checker for the entire class~\cite{Welsch:backward12}, we regard it as safe if the used API is compatible for the other version in the current usage context. We make this trade-off because developers often embrace changes, making multiple versions incompatible to each other~\cite{bogart:backward}. To save build time and space,  we include multiple versions of the files from the same library only if they are incompatible with each other, instead of maintaining multiple versions for the same library at the same time. To save time for analysis, we only consider the API calls when it has the possibility to generate `dependency hell', since there is no need to check the dependency issue if the libraries are consistent used in the system with a single version.
